A Bioconductor Workflow for Processing and Analysing Spatial Proteomics Data

### 2016-09-08 bioc-workflow.Rmd
added svm params

```{r loadpdRes, include=FALSE}
load("Data/fusionparams.rda")
w <- table(getMarkers(hl, verbose = TRUE))
w <- 1/w[names(w) != "unknown"]
```

```{r optimise, eval=FALSE}
w <- table(getMarkers(hl, verbose = TRUE))
w <- 1/w[names(w) != "unknown"]

>>>>

```{r loadpdRes, echo=FALSE}
svmf <- dir(extdatadir, full.names = TRUE,
              pattern = "bpw-svmopt.rds") 
params <- readRDS(svmf)
```
```{r optimise, eval=FALSE}
w <- table(getMarkers(hl, verbose = TRUE))
w <- 1/w[names(w) != "unknown"]
